Inferring neural networks from fluorescent calcium imaging using partial correlation and sample weighting

### 2014-06-06 article.tex
wording

 %\usepackage{rotating}% for sideways figures and tables
% \usepackage{longtable}% for long tables

@@

\begin{abstract}
Understanding how the brain works is a key to understand and to treat
brain pathologies and disorders such as Parkinson's disease, epilepsy.
Retrieving the connectomes, neurons connectivity map, will shed new lights on
the anatomical and functional connectivity of the brain.
In the context of the Connectomics challenge, we propose a pre-processing and
a simple approach in order to achieve a high performance inference of the
connectivity network.
We put in perspective our method by comparing with other inference method such
as GTE [], another method proposed to infer a neural network from calcium
fluorescent imaging, and Genie3 [], a tree-based approach very competitive
in several gene inference challenge (i.e. DREAM4 and DREAM5).

@@

\begin{keywords}
Network inference - Partial correlation - Precision matrix - GENIE3
\end{keywords}

@@

% BG : brain, complex organ
The human brain is a complex biological organ, which is formed by 100
billions of neurons with 7000 synaptic connections on average. Inferring the
neuron connectivity network through dissection would be an impossible
and a daunting task. Cutting edge optical devices [todo cite] allow to track
simultaneously the neural activity of thousands of neurons through a fluorescent
calcium indicator.

From those observational data, the neural connectivity inference consists in
highlighting direct relationships between neurons. However, those imaging
systems have a sampling rate smaller than the neuron firing speed and are
limited to two dimensional image, while the neuronal network is a
three dimensional structure, which may lead to superpose the observed activity
of different neurons. Furthermore, the decay of the fluorescent calcium signal
is slower than its rise.

% Introduce notation + goal in mathematical score
% TODO check convention for y_{ij}
One way to emphasize the connections between neurons is to represent them by a
(un)directed graph with $p$ nodes: each node represents a neuron, and each
edge $y_{ij}$ represents a direct link from neuron  $i$ to neuron $j$. If the
graph is undirected, then $y_{ij}$ is equal to $y_{ji}$  for all $i,j$.
The unsupervised task may be formulated as:
\textit{Given $X \in \mathcal{R}^{n \times p}$  a set of $p$ time series of
fluorescent calcium concentration of size $n$ from $p$ neurons, the goal is to
infer the connectivity graph $y \in \left\{0, 1\right\}^{p \times p}$.}
The main challenge in the inference of the network $y$
is to distinguish direct from indirect interactions \cite{de2004discovery}.
For instance with the simple interaction graph $A \rightarrow B \rightarrow C$,
we want to distinguish direct interactions $A \rightarrow B$ and $B \rightarrow C$
from the indirect interaction $A \rightarrow C$.

@@

% Solution
In this paper, we describe a simple and a theoretically grounded approach
based on partial correlation to infer the neural connectivity network.
This is also the winning method of the Connectomics challenge
\footnote{\url{http://connectomics.chalearn.org/}}. For reproducibility, the
source code of the method is available at
\url{https://github.com/asutera/kaggle-connectomics} under BSD 3-clauses
license.

\section{Methodology}
\section{Signal filtering} \label{sec:filter}
% Explain why we need to filter
% TODO

% Filtering methodology
Prior inferring the network, the fluorescent calcium time series are smoothed
using several linear and non linear filters. A low-pass filter, a high-pass
filter and a non linear hard-thresholding based filter are
applied for each possible time step $t$
% TODO fix first equation is wrong due notation change
\begin{align}
X^\prime_{t,i} &= \sum_{l=-3}^2 c_l^k X_{t+l,i} \forall i, \\
X^{\prime\prime}_{t,i} &= X^{\prime}_{t,i} - X^{\prime}_{t-1,i} \forall i, \\
X^{\prime\prime\prime}_{t,i} &= {X^{\prime\prime}_{t,i}}^{0.9} I(X^{\prime\prime}_{t,i} \geq f_3) \forall i,
\end{align}
where the $c_l^k$ coefficients were taken in one of the four following tuples
$\left\{c_l^1\right\}=(0, 0, 1, 1, 1, 1)$,
$\left\{c_l^2\right\}=(0, 0, 1, 1, 1, 0)$,
$\left\{c_l^3\right\}=(1, 1, 1, 1, 0, 0)$ or
$\left\{c_l^4\right\}=(0.4, 0.8, 1, 1, 0, 0)$ and $f_3$ is a parameter
of the hard-threshold filter.

Then we apply on all remaining timesteps $T$ a non-linear filter based on the current
activity of the systems in order to favor the association measure when
a medium size set of neurons are firing together, while artificially
reducing the association measure in case of extreme network activity,
i.e. high when a network firing is happening and low when no neuron is
active:
\begin{align}
a_t &= \sum_{i=1}^p X^{\prime\prime\prime}_{t,i} +
                   \frac{1}{2} X^{\prime\prime\prime}_{t-1,i} \forall t \in T\\
r_t &= \frac{a_t}{\max_{l \in T}{a_l}} \\
X^{\prime\prime\prime\prime}_{t,i} &=
\left\{
  \begin{array}{l}
    1  : r_t < 0\\
    {(X^{\prime\prime\prime}_{t,i} + 1)^{(a_t^{-1} + 1)}}^{g(r_t)} : r_t \geq 0
  \end{array}
\right.
\end{align}
where $g(x) = b_1 I(f_4 < x < f_5) + b_2  I(f_5 \leq x < f_6) +
b_3 (I(x\leq f_4) + I(f_ 6 \leq x))$ is a piecewise continuous function of
parameters $b_1, b_2, b_3, f_4, f_5, f_6$. The coefficient were tuned
for each set of coefficient $\left\{c_l^k\right\}$.

@@

\subsection{Network inference through partial correlation}
\label{sec:inference}

@@

Each neuron signal $i$ is a random continuous variable $X_i$,
which follows a probability density function $p_\mathcal{X_i}(x_i)$.
Two neurons $X_i$, $X_j$ will be said conditionally independent
to a set of neurons $X_1,\ldots,X_p \backslash \left\{X_i, X_j\right\}$, denoted
by  $X_i \perp X_j | X_1,\ldots,X_p \backslash \left\{X_i, X_j\right\}$,  if
\begin{align*}
&p_{X_i, X_j | X_1,\ldots,X_p \backslash \left\{X_i, X_j\right\}}
    (x_i, x_j | x_1,\ldots,x_p \backslash \left\{x_i, x_j\right\}) \\
=&p_{X_i | X_1,\ldots,X_p \backslash \left\{X_i, X_j\right\}}
    (x_i | x_1,\ldots,x_p \backslash \left\{x_i, x_j\right\})
p_{X_j | X_1,\ldots,X_p \backslash \left\{X_i, X_j\right\}}
    (x_j | x_1,\ldots,x_p \backslash \left\{x_i, x_j\right\})
\end{align*}
for all real numbers $x_1,\ldots,x_p $ such that
$p_{X_1,\ldots,X_p \backslash \left\{X_i, X_j\right\}}
(x_1,\ldots,x_p \backslash \left\{x_i, x_j\right\}) > 0$. Note that this
reciprocal is true only under additional hypotheses.

@@

\subsection{Stacking partial correlation matrix}
\label{sec:stacking}

% Speak about why averaging
The quality of the signal filtering and network inference is dependent upon
good hyper-parameter selection, which are themselves dependent on the properties
of the targeted network and measurement conditions, e.g. signal to noise ratio.
Ensemble methods are known to improve robustness with respect to parameter
selection [todo cite] and improve performance [todo cite].
A weighted average $y_{stack}$ of partial correlation matrices was made
by varying uniformly the hard-threshold value (parameter $f_3$) and the design
of the low-pass filter (coefficients $c_l$). The stacked connectivity score
matrix $y_{stacking}$ is given by
\begin{align}
y_{stack} =  \dfrac{1}{\sum_{k\in\{1,..,4\}} w_k |T_k|} \sum_{k=1}^{k=4}  w_k \sum_{f_3 \in T_k} f(X, k, f_3)
\end{align}
where $f(X, k, f_3)$ gives the predicted adjacency matrix, i.e. applies the
filtering and inference methodologies (as described
in sections \ref{sec:filter} and \ref{sec:inference}), with a  given value
$f_3$ for the hard-threshold among a set of thresholds $T_k$ of size $|T_k|$
and the $k^{th}$ low-pass filter pattern associated to a weight $w_k$ whose
values are $w_1 = 0.01 , w_2 =1, w_3 = 0.7, w_4 = 0.9$.

\subsection{Causal discovery methodology}
% Introduce a custom solution to make the Y matrix asymmetric
% Introduce directivity
Since the partial correlation is a symmetric measure, the causal mechanism behind the
interaction ($A$ directly causes $B$, $B$ directly causes $A$ or both) can not
be inferred\footnote{Also note that two other causal mechanisms might be
implied while having a non-zero partial coefficient: (i) a pair of variables
is induced by a common (hidden) variable; (ii) $A$ (respectively $B$) is
conditionally correlated to a hidden variable affecting $B$ (resp. $A$)
\cite{de2004discovery}.} directly from a symmetric adjacency matrix.

By ignoring the directivity, we systematically
make a true positive and a false positive for direct link (see a more detailed
discussion about the chosen metric in section \ref{sec:metric}). Therefore,
performance might be improved by predicting an asymmetric adjacency matrix.
Hoping to orientate correctly the most obvious directed links, we attempt to
retrieve some causal information, i.e. the directivity of the links, by computing
and stacking with our symmetric adjacency matrix a matrix of pairwise activation
heuristics. This method computes an anti-symmetric activation score $z_{ij}$
based the variation of fluorescence signal of a neuron $j$ due to a neuron $i$
over all timesteps:
\[
z_{ij} = \sum_{t=1}^n I(X_{t+1,j} - X_{t, i} \in [f_1, f_2]) -  I(X_{t+1,i} - X_{t, j} \in [f_1, f_2])
\]
where $f_1$ and $f_2$ are parameters of the method and $I$ is the
indicator function. % TODO say that we use only the 3 first filters for this

% TODO speak that we should set the diagonal to the minimum to gain some
% performance.

\section{Experiments}
% Datasets
To assess our method, we have used four datasets provided by the organizer
of the Connectomics challenge : normal-1, normal-2, normal-3, normal-4. Those
datasets are time series of size $n=179500$ of image calcium from simulated
neuronal network \cite{stetter2012model} with $p=1000$ neurons. The networks
to inferred have around 15000 arcs or a density of $0.15\%$.

% Metrics : ROC AUC and AUPRC
The network inference task can be viewed as a binary classification task
where one have to correctly classified the presence or the absence of edges
in the connectivity graph. Given the ground true network
$y_{i,j} \in \left\{0, 1\right\}$, the connectivity score matrix
$\hat{y}_{i,j} \in \mathcal{R}$ inferred by a given modeling technique
can be thresholded by a value $\tau \in \mathcal{R}$ to evaluate its performance. In this
context, we first define the notion of
true positive $tp(\tau) = \sum_{i=1}^p \sum_{j=1}^p I(y_{i,j} = 1, \hat{y}_{i,j} \geq \tau)$,
true negative $tn(\tau) = \sum_{i=1}^p \sum_{j=1}^p I(y_{i,j} = 0, \hat{y}_{i,j} < \tau)$,
false negative $fn(\tau) = \sum_{i=1}^p \sum_{j=1}^p I(y_{i,j} = 1, \hat{y}_{i,j} < \tau)$ and
false positive $fp(\tau) = \sum_{i=1}^p \sum_{j=1}^p I(y_{i,j} = 0, \hat{y}_{i,j} \geq \tau)$,
which is also called the confusion matrix.

We assess the accuracy of the network inference using the area under
the ROC curve (ROC AUC) obtained by varying the threshold
$\tau$ of the true positive rate $tpr(\tau) = \frac{tp(\tau)}{tp(\tau) + fn(\tau)}$
as a function of the false positive rate
$fpr(\tau) = \frac{tn(\tau)}{tn(\tau) + fp(\tau)}$. In section (TODO ref),
we also compare the same methods with the area under the precision-recall
(AUPRC) curve, an information retrieval metrics, obtained by varying the threshold
$\tau$ of the precision $P(\tau) = \frac{tp(\tau)}{tp(\tau) + fp(\tau)}$
as a function of the recall $R(\tau) = \frac{tp(\tau)}{tp(\tau) + fn(\tau)}$.

\subsection{Data filtering and Signal distribution}

\subsection{Inference of neuronal network}

\begin{table}[htb]
\centering
\caption{Improvement of each stage of our approach Note that we choose the
         \textit{best} threshold for stages 1 to 4.}
\begin{tabular}{*{5}{l}}
\toprule
Stage               & normal-1 & normal-2 & normal-3 & normal-4 \\
\midrule
Inverse correlation & & & & \\
Pre-processing      & & & & \\
PCA                 & & & & \\
Weighting           & & & & \\
Averaging           & & & & \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}[htb]
\centering
\caption{Comparison with other methods}
\begin{tabular}{*{5}{l}}
\toprule
Methods             & normal-1 & normal-2 & normal-3 & normal-4 \\
\midrule
Correlation         & & & & \\
Partial correlation & & & & \\
Our approach        & & & & \\
GENIE3              & & & & \\
GTE                 & & & & \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Discussion about the metric}
\label{sec:metric}

@@

% Possible extensions
% partial autocorrelation function (sometimes "partial correlation function")
% conditional independence test
% Speak about the complexity and parallelization of the methods

>>>>

 %\usepackage{rotating}% for sideways figures and tables
\usepackage{longtable}% for long tables

@@

\begin{abstract}
Understanding how the brain works is a key to understand and to treat
brain pathologies and disorders such as Parkinson's disease, epilepsy.
Retrieving the connectomes, neurons connectivity map, will shed new lights on
the anatomical and functional connectivity of the brain.

In the context of the Connectomics challenge, we propose a simple algorithm made of four stages to achieve a network inference of high quality.

We put in perspective our method by comparing with other inference method such as GTE [], another method proposed to infer a neural network from calcium fluorescent imaging, and Genie3 [], a tree-based approach very competitive in several gene inference challenge (i.e. DREAM4 and DREAM5).\\

@@

\begin{keywords}
Network inference - Precision matrix - GENIE3
\end{keywords}

@@

% BG : brain, complex organ
Understanding how the brain works is a key to understand and to treat
brain pathologies and disorders such as Parkinson's disease and epilepsy.
Retrieving the connectomes, neurons connectivity map, will shed new lights on
the anatomical and functional connectivity of the brain. However,
the human brain is a complex biological organ, which is formed by 100
billions of neurons with 7000 synaptic connections on average. Inferring the
neuron connectivity network through dissection would be an impossible
and a daunting task.

Cutting edge optical devices [todo cite] allows to track simultaneously
the neural activity of thousands of neurons through the fluorescent
calcium indicator.
From those observational data, the neural connectivity inference consists in
highlighting direct relationships between neurons. However, those imaging
systems have a sampling rate smaller than the neuron firing speed and are
limited only two dimensional image, which may lead to superpose the activity
of different neurons. Furthermore, the decay of the fluorescent calcium signal
is slow compare to its rise.

@@

% Solution
In this paper, we describe a simple and a theoretically grounded approach
based on partial correlation to infer the neural connectivity network.
This is also the winning method of the Connectomics challenge [todo cite].

\section{Signal filtering methodology}
\label{sec:filter}
% Explain why we need to filter
% TODO

% Filtering methodology
Prior inferring the network, the fluorescent calcium time series are smoothed
using several linear and non linear filters. A low-pass filter, a high-pass
filter and a non linear hard-thresholding based filter are
applied for each possible time step $t$
\begin{align}
X^\prime_{t,i} &= \sum_{l=-3}^2 c_l^k X_{t+l,i} \forall i, \\
X^{\prime\prime}_{t,i} &= X^{\prime}_{t,i} - X^{\prime}_{t-1,i} \forall i, \\
X^{\prime\prime\prime}_{t,i} &= {X^{\prime\prime}_{t,i}}^{0.9} I(X^{\prime\prime}_{t,i} \geq f_3) \forall i,
\end{align}
where the $c_l^k$ coefficients were taken in one of the four following tuples
$\left\{c_l^1\right\}=(0, 0, 1, 1, 1, 1)$,
$\left\{c_l^2\right\}=(0, 0, 1, 1, 1, 0)$,
$\left\{c_l^3\right\}=(1, 1, 1, 1, 0, 0)$ or
$\left\{c_l^4\right\}=(0.4, 0.8, 1, 1, 0, 0)$ and $f_3$ is a parameter
of the hard-threshold filter.

Then we apply a non-linear filter based on the current
activity of the systems in order to favor the association measure when
a medium size set of neurons are firing together, while artificially
reducing the association measure in case of extreme network activity,
i.e. high when a network firing is happening and low when no neuron is
active:
\begin{align}
a_t &= \sum_{i=1}^p X^{\prime\prime\prime}_{t,i} +
                   \frac{1}{2} X^{\prime\prime\prime}_{t-1,i} \forall t \in T\\
r_t &= \frac{a_t}{\max_{l \in T}{a_l}} \\
X^{\prime\prime\prime\prime}_{t,i} &=
\left\{
  \begin{array}{l}
    1  : r_t < 0\\
    {(X^{\prime\prime\prime}_{t,i} + 1)^{(a_t^{-1} + 1)}}^{g(r_t)} : r_t \geq 0
  \end{array}
\right.
\end{align}
where $g(x) = b_1 I(f_4 < x < f_5) + b_2  I(f_5 \leq x < f_6) +
b_3 (I(x\leq f_4) + I(f_ 6 \leq x))$ is a piecewise continuous function of
parameters $b_1, b_2, b_3, f_4, f_5, f_6$. The coefficient were tuned
for each set of coefficient $\left\{c_l^k\right\}$.

@@

\section{Network inference methodology}
\label{sec:inference}
% Introduce notation + goal in mathematical score
% TODO check convention for y_{ij}
One way to emphasize the connections between neurons is to represent them by a
(un)directed graph with $p$ nodes: each node represents a neuron, and each
edge $y_{ij}$ represents a direct link from neuron  $i$ to neuron $j$. If the
graph is undirected, then $y_{ij}$ is equal to $y_{ji}$  for all $i,j$.
The unsupervised task may be formulated as:
\textit{Given $X \in \mathcal{R}^{n \times p}$  a set of $p$ time series of
fluorescent calcium concentration of size $n$ from $p$ neurons, the goal is to
infer the connectivity graph $y \in \left\{0, 1\right\}^{p \times p}$.}
The main challenge in the inference of the network $y$
is to distinguish direct from indirect interactions \cite{de2004discovery}.
For instance with the simple interaction graph $A \rightarrow B \rightarrow C$,
we want to distinguish direct interactions $A \rightarrow B$ and $B \rightarrow C$
from the indirect interaction $A \rightarrow C$.

@@

Let us consider that each neuron signal $i$ is a random continuous variable $X_i$
which follows a probability distribution $p_{X_i}$ and let us denote by $p_{X_i,X_j|\mathcal{Z}}$ the 
joint probability distribution of neurons $X_i$ and $X_j$ conditioned on a subset of variables $\mathcal{Z}$ (eventually empty). Let us define $\mathcal{V}$
the set of all neurons $X_1, ..., X_p$ and $\mathcal{V}^{-i,j}$ the same set without
neurons $X_i$ and $X_j$.

Each neuron signal $i$ is a random continuous variable $X_i$,
which follows a probability density function $p_\mathcal{X_i}(x_i)$.
Two neurons $X_i$, $X_j$ will be said conditionally independent
to a set of neurons $\mathcal{V}^{-i,j}$, denoted
by  $X_i \perp X_j | \mathcal{V}^{-i,j}$,  if $p_{X_i,X_j|\mathcal{V}^{-i,j}} = p_{X_i|\mathcal{V}^{-i,j}}  p_{X_j|\mathcal{V}^{-i,j}} $.
%for all real numbers $x_1,\ldots,x_p $ such that
%$p_{X_1,\ldots,X_p \backslash \left\{X_i, X_j\right\}}
%(x_1,\ldots,x_p \backslash \left\{x_i, x_j\right\}) > 0$. Note that this
%reciprocal is true only under additional hypotheses.

@@

\section{Stacking methodology}
\label{sec:stacking}
% Speak about why averaging
%In order to improve performance, we stacked the partial correlation matrix

Our first guess was that introduce an ensemble method would improve performance
[cite papers which praise ensemble methods]. Among all parameters of our method,
we choose to average over two parameters, i.e. over multiple combinations of the
hard-threshold value $f_3$ and the pattern of the low-pass filter $c_l$. In order to 
free ourself from the choice of a probability distribution for the $(f_3,c_l)$ combinations,
we choose a uniform distribution for the threshold distribution (in a given interval of 
values) within each filtering process and perform a weighted average for the low-pass 
filter pattern. Formally, the stacked predicted adjacency matrix $y_{stacking}$ can be formulated by

\begin{align}
y_{stacking} =  \dfrac{1}{\sum_{k\in\{1,..,4\}} w_k |T_k|} \sum_{k=1}^{k=4}  w_k \sum_{f_3 \in T_k} f(X, k, f_3)
\end{align}
where $f(X, k, f_3)$ gives the predicted adjacency matrix, i.e. applies the filtering 
and inference methodologies (as described in sections \ref{sec:filter} and \ref{sec:inference}), 
with a  given value $f_3$ for the hard-threshold among a set of thresholds $T_k$ 
of size $|T_k|$ and the $k^{th}$ low-pass filter pattern associated to a weight $w_k$ 
whose values are $w_1 = 0.01 , w_2 =1, w_3 = 0.7, w_4 = 0.9$.

\section{Causal discovery methodology}
% Introduce a custom solution to make the Y matrix asymmetric
% Introduce directivity
Since the partial correlation is a symmetric measure, the causal mechanism behind the
interaction ($A$ directly causes $B$, $B$ directly causes $A$ or both) can not
be directly inferred\footnote{Also note that two other causal mechanisms might be
implied while having a non-zero partial coefficient: (i) a pair of variables
is induced by a common (hidden) variable; (ii) $A$ (respectively $B$) is
conditionally correlated to a hidden variable affecting $B$ (resp. $A$)
\cite{de2004discovery}.} from a symmetric adjacency matrix.

By not taking into account the directivity for directed links, we systematically 
make a true positive and a false positive for such links (see a more detailed 
discussion about the chosen metric in section \ref{sec:metric}). Therefore, 
performance might be improved by predicting an asymmetric adjacency matrix.  
Hoping to orientate correctly the most obvious directed links, we attempt to 
retrieve some causal information, i.e. the directivity of the links, by computing 
and stacking with our symmetric adjacency matrix a matrix of pairwise activation 
heuristics. This method computes an anti-symmetric activation score $z_{ij}$ 
based the variation of fluorescence signal of a neuron $j$ due to a neuron $i$ 
over all timesteps:
\[
z_{ij} = \sum_{t=1}^n I(X_{t+1,j} - X_{t, i} \in [f_1, f_2]) -  I(X_{t+1,i} - X_{t, j} \in [f_1, f_2])
\]
where $f_1$ and $f_2$ are parameters of the method and $I$ is the
indicator function. % TODO say that we use only the 3 first filters for this

\section{Empirical experiments}
In this section, we will present some experiments on challenge datasets to show 
the good performance of our method and compare it to other inference methods. 
Since it was the metric used during the challenge, we will compare inference methods
regarding the area under the ROC curve. However, we will discuss about this in section
\ref{sec:metric}.

\paragraph{Datasets \\}
To assess the quality of our method, we use four network, denoted as \textit{normal-\{1,2,3,4\}}, similar to networks, i.e., the same number of neurons, used to rank challenge participants. Note that our parameter tuning was mainly on \textit{normal-1} dataset and partly on \textit{normal-4} dataset, therefore it may justify why these networks are better retrieved despite the fact that some might be simpler to infer.

\subsection{Data filtering}
\subsection{Signal distribution}
\subsection{ROC AUC results}
\paragraph{Improvement of each stage of our approach\\}

\begin{table}[htb]
\centering
\begin{tabular}{|c|c||c|c|c|c|c|c|} \hline
\# & Stage & normal-1 & normal-2 & normal-3 & normal-4 \\ \hline
1 & Inverse correlation & & & & \\ \hline
2 & Pre-processing & & & &\\ \hline
3 & PCA & & & &  \\ \hline
4 & Weighting & & & &  \\ \hline
5 & Averaging & & & &  \\ \hline

\end{tabular}
\end{table}

Note that we choose the \textit{best} threshold for stages 1 to 4.
\paragraph{Comparison with other methods\\}

\begin{table}[htb]
\centering
\begin{tabular}{|c|c||c|c|c|c|} \hline
\# & Stage & normal-1 & normal-2 & normal-3 & normal-4 \\ \hline
1 & Inverse correlation & & & &\\ \hline
2 & Correlation & & & &\\ \hline
3 & GENIE3 & & & & \\ \hline
4 & GTE & & & & \\ \hline

\end{tabular}
\end{table}
\subsection{Discussion about the metric}
\label{sec:metric}

@@

% Possible extensions
% partial autocorrelation function (sometimes "partial correlation function")
% conditional independence test
